Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-04 ms.tex
Add interpretation to wide-field effects
from a805428:
============

In ms.tex,

(*) Add interpretation to wide-field effects under section "Wide-field
measurements"

\citet{thy13} have found evidence of this feature in their statistical models. In line with our reasoning, they attribute it to an increase in solid angles subtended by delay bins closer to the horizon limits thereby, enhancing the resulting integrated emission. \citet{pob13} also find a similar ``edge brightening'' feature which they attribute to emission from the Galactic plane near the horizon. From their discussion, it is unclear what fraction of power in that feature arises from such wide--field effects.

>>>>

We interpret this is due to equal--sized delay bins subtending larger solid angles near the horizon thereby containing larger integrated emission. An alternate, but equivalent, interpretation is that baseline vectors (including those with largest lengths) are foreshortened towards the horizon along their orientation. Thus, they become sensitive to larger angular scales that match the inverse of their foreshortened baseline lengths.

\citet{thy13} have found evidence of this feature in their statistical models. In line with our reasoning, they attribute it to a steep rise in solid angles subtended by delay bins near the horizon limits. \citet{pob13} also find a similar ``edge brightening'' feature which they attribute to emission from the Galactic plane near the horizon. From their discussion, it is unclear what fraction of power in that feature arises from such wide--field effects.
